Estimating duration in the presence of misclassification

### 2024-03-09 introduction.tex
Move Overleaf comments on prev version across

For large parts of the pandemic, community testing was widely available in the UK.
The number of tests conducted varied over time and space, for a variety of known and unknown reasons.
These include: policy on who is eligible for testing, the availability of tests, and the willingness of individuals to be tested.
Therefore, fluctuations in the number of positive tests may not reflect changes in the true incidence of the disease.
However, there were many test results, allowing detailed analyses to be performed, including stratification by small geographic areas or age groups.

Seroprevalence surveys indicate the proportion of the population that have been infected with the disease.
Prior infection is more common than current infection, hence seroprevalence estimation requires a smaller sample size than current prevalence.
However, there is a delay between infection and the development of antibodies, hence seroprevalence is not a real-time measure of the burden of the disease.
Furthermore, seroprevalence data is normally based on convenience samples (\eg blood donors) who are not representative of the general population.

@@

In the UK, SPI-M-O (Scientific Pandemic Influenza Group on Modelling, Operational sub-group) was a sub-committee of SAGE (the Scientific Advisory Group for Emergencies), using this type of models to generate evidence for policy development~\autocite{medleySPIM,govSPIMO}.
For example, each of the stages of lifting the lockdown in 2021 was supported by  modelling studies informing the government's decision~\autocite{sageEvidence}.

@@

The nowcasting estimates were mainly based on mechanistic and semi-mechanistic models with a wide variety of data sources.
The mechanistic models commonly incorporated multiple data sources, known as \emph{data synthesis}, a technique reviewed by \textcite{birrellEvidence}.
The models used were reviewed by \textcite{royalSocietyRnumber} (see appendix 2 of that review for details of the specific implementations).

>>>>

For large parts of the pandemic, community testing was widely available in the UK.
However, it does not test a random sample of the population.
The number of tests conducted varied over time and space, for a variety of known and unknown reasons.
These include: policy on who is eligible for testing, the availability of tests, and the willingness of individuals to be tested.
Therefore, fluctuations in the number of positive tests may not reflect changes in the true incidence of the disease.
The large number of tests conducted allowed detailed analyses to be performed, including stratification by small geographic areas or age groups, although this does not solve the issue of the biases present.

Seroprevalence surveys estimate the proportion of the population previously infected.
Prior infection is more common than current infection, hence seroprevalence estimation requires a smaller sample size than current prevalence.
However, there is a delay between infection and the development of antibodies, hence seroprevalence is not a real-time measure of the burden of the disease.
Furthermore, seroprevalence data is normally based on convenience samples (\eg blood donors) who are not representativeness of the wider population is unclear.

@@

In the UK, SPI-M-O (Scientific Pandemic Influenza Group on Modelling, Operational sub-group) was a sub-committee of SAGE (the Scientific Advisory Group for Emergencies), generating evidence based on infectious disease modelling for policy development~\autocite{medleySPIM,govSPIMO}.
For example, each of the stages of lifting the lockdown in 2021 was supported by  modelling studies informing the government's decision~\autocite{sageEvidence}.

@@

The nowcasting estimates were based on mechanistic and semi-mechanistic models with a wide variety of data sources.
The mechanistic models commonly incorporated multiple data sources, known as \emph{data synthesis}, a technique reviewed by \textcite{birrellEvidence}.
The models used were reviewed by \textcite{royalSocietyRnumber} (see appendix 2 of that review for details of the specific implementations).
